Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}

### 2018-07-30 nir_companions.tex

The list of observations obtained with CRIRES are provided in Table~\ref{tab:observations}. The number of artefacts are how many of the 32 individual detector nod spectra that were found to contain artefacts, see Section \ref{\label{subsubsec:reduction}}. The SNR is calculated with the formula \(\textrm{SNR} = \frac{\mu}{\sigma}\) where $\mu$ and $\sigma$ are the mean and standard deviation in the continuum of detector 2 between 2130 and 2134 (see Fig.~\ref{fig:spectral_example}.
The estimated RV values for the host and companion at the time of each observation are calculated using Equation~\ref{eq:rv_equation} using the best known orbital parameters and the companion masses from Tables~\ref{tab:starparams} and \ref{tab:orbitparams}. For hosts with multiple companions the RV value is for the largest companion only, i.e. {HD 202206}B and {HD 168443}c. The RV difference between the host and the companion \(rv_2\) = (\(RV_2 - RV_1\)) is parameter used in the binary model from Sect.~\ref{subsubsec:binary-model}. }

>>>>

{\rd The list of observations obtained with CRIRES are provided in Table~\ref{tab:observations}. The number of artefacts found in the 32 individual detector nod spectra for each observation are listed as artefacts, see Section~\ref{subsubsec:reduction} for more details. The SNR is calculated with the formula \(\textrm{SNR} = \frac{\mu}{\sigma}\) where $\mu$ and $\sigma$ are the mean and standard deviation in the continuum of detector 2 between 2130 and 2134 (see Fig.~\ref{fig:spectral_example}).
The estimated RV values for the host and companion at the time of each observation are calculated using Equation~\ref{eq:rv_equation} using the best known orbital parameters and the companion masses from Tables~\ref{tab:starparams} and \ref{tab:orbitparams}. For hosts with multiple companions the RV value is for the largest companion only, i.e. {HD 202206}B and {HD 168443}c. The RV difference between the host and the companion \(rv_2\) = (\(RV_2 - RV_1\)) is parameter used in the binary model from Sect.~\ref{subsubsec:binary-model}. }
